%template:
%\nextItem decision & reason
\nextItem More information about minutes. & Provide more formal information about decisions. Reduce chance of misunderstanding.
\nextItem More technical issues in appendix. & Provide more formal information about decisions. Reduce chance of misunderstanding.
\nextItem Send customer link with notes. & Customer demand.
\nextItem Research and use Testflight. & Customer proposal.
\nextItem Scaling decision. & We are probably not able to make application for rock concert in 13 weeks.
\nextItem Not focusing much on testing. & Customer proposal.
\nextItem Milestones are not connected to sprints. Additional milestones can be added. We can use hard-coding for milestones. & Customer proposal.
\nextItem We have to create a better agenda. & To be more efficient during meetings.
\nextItem We will use Gantt chart and burn-down chart. & To check if we are working according to schedule.
\nextItem Documentation should show the changes not to redefinining it. & To track our work progress.
\nextItem We have decided to end our Sprint0 prematurely and start Sprint1 on Monday 2 September. & We want to start working on core of the project asap.
\nextItem Be more active and independent. Try to make decisions. Event a part of team can make decisions, not whole team is necessary. & Not everyone has to decide about everything.
\nextItem Instead of story points we will use hours. We will fill worked hours on story into Gravity. & Gravity supports only hours, it is useful to compare estimate hours and real hours.
