\newcommand{\meetingNumber}{3}
\newcommand{\meetingPlace} {Gloshaugen, Room}
\newcommand{\meetingDate}  {29 August 2013}
\newcommand{\meetingTime}  {16:00}
\newcommand{\membersPresent} {  Peder Kongelf,
                                Agnethe Soraa,
                                Tomas Dohnalek,
                                Jan Bednarik,
                                Milos Jovac}
\newcommand{\membersMissing} {(none)}
\newcommand{\summary} {
We started with discussing the meeting minutes from the last meeting. Customer suggested we should put more information in meeting minutes, even the technical ones (possibly in appendix). We presented to the customer the collaboration tool Gravity. Customer suggested to use certain tags such as \textit{admin}, \textit{research}, \textit{report}, \textit{tools/technologies}, etc. Customer also suggested to use the HockeyApp service to distribute the application. 

We then presented our milestones but customer did not agree and advised us to take more agile approach. Customer suggested a few specific milestones and tasks, we will utilize them. The utilization of Gantt chart and burndown chart was suggested in order to keep track on whether we are behind plan. We moved on to discuss the report. According to the customer the report should display changes so we should not rewrite the content. We might also use more diagrams and charts.

We then discussed the user stories. We should present the new roles e.g. \textit{concert manager}. During the effort estimation we will use hours instead of points. customer then decided how important each story is.
}
\newcommand{\nextMeeting} {2 September 2013, exact time TBA}
\newcommand{\meetingEnd} {18:00}
