\newcommand{\meetingNumber}{5}
\newcommand{\meetingPlace} {Gloshaugen, Room}
\newcommand{\meetingDate}  {27 September 2013}
\newcommand{\meetingTime}  {10:15}
\newcommand{\membersPresent} {  Anh Nguyen Duc,
                                Agnethe Soraa,                                
                                Jan Bednarik,
                                }
\newcommand{\membersMissing} {Tomas Dohnalek,
								Milos Jovac}
\newcommand{\summary} { We started the meeting with the demonstration of the prototype 2 using the YouTube video. Then we discussed the work breakdown structure. The supervisor suggested that that each level of the WBS tree should be consistent and that we should not mix up the activities with deliverables. the connection between user stories and requirements were then discussed and the decision to better connect the non-functional requirements with the "Architecture" section in the project report was made. We also discussed the requirements with the advisor. He suggested that we should make the list of strict requirements and agree with the customer on approving of them. The main reason for doing so is the fact the customer started to add and/or adjust the requirements which might be too risky for the team as we lack enough resources (mainly the time). We also asked the supervisor for the advice who to talk with about the image processing. The supervisor will suggest the proper person and/or department.
}
\newcommand{\nextMeeting} {4 October}
\newcommand{\meetingEnd} {11:30}
