%\caption{User stories selected for Sprint 1.}
  \label{tab:sprint1stories}
 \def\arraystretch{1.25}
 
\begin{longtable}{ccXcc}

\toprule[1mm]
\multirow{2}{*}{\textbf{ID}} &
\multirow{2}{*}{\textbf{Ref.}} & \multirow{2}{*}{\textbf{Description}} & \multicolumn{2}{c}{\textbf{Hours}} \\
 					& & & \textbf{Est.} & \textbf{Sp.} \\
%\textbf{ID} 	& \textbf{Description} 									& \textbf{Est.} & \textbf{Sp.} \\
\midrule
% === IMPLEMENTATION ==========================
\textbf{314} 	& \refreq{M6}
	& {\bf As a developer I need to put "Hello World" project to gitHub and pull it to every group member's local storage} 	& 	18	& \textbf{ 4.7} \\
				&& Create folder on gitHub account named "source".	&  &  \\
				&& Install ADT and Eclipse to our local computers. 	&  &  \\
				&& Create new Android Project and push it to gitHub. 	&  &  \\


\textbf{313} 	& \refreq{C1}
	& {\bf As a developer I need to establish basic communication protocol between client \& server.} 	& 		4	& \textbf{4} \\
	
\textbf{312} 	& \refreq{C1}
	& {\bf As a developer I need to make the server able to listen for the clients.} 	& 	30	& \textbf{22} \\
				&& Research about server sockets.	&  &  \\
				&& Implement server listener.	&  &  \\
				&& Create the moc client. &  &  \\
				&& Connect with mock client. &  &  \\
	
\textbf{335} 	& \refreq{M6}
	& {\bf As a developer I need to make the server send one command to one client. } 	& 		4	& \textbf{4} \\

\textbf{336} 	& \refreq{M6}
	& {\bf As a developer I need to make the client receives one command. } 	& 	2	& \textbf{2} \\

\textbf{353} 	& \refreq{M6}
	& {\bf As a developer I need to make client receive commands from the server.} 	& 	4		& \textbf{4} \\

\textbf{334} 	& \refreq{M6}
	& {\bf As a developer I need to make the client "play" one command (white light 10 seconds). } 	& 		4.5	& \textbf{4.5} \\

\textbf{290} 	& \refreq{M3}
	& {\bf As a developer I want to see the number of connected devices to the server. } 	& 		0.5	& \textbf{0.5} \\

\textbf{262} 	&& {\bf As a developer I need to research the TestFlightApp. } 	& 		6	& \textbf{2.5} \\
				&& Figure out whether to use HockeyApp or TestFlight&  &  \\
				&& Research TestFlight	&  &  \\
\textbf{267} 	&& {\bf As developer I need to set up testflight. } 	& 		5	& \textbf{8} \\

\midrule
% === DOCUMENTATION ==========================
\textbf{343} 	&& {\bf As a student I have to work on Project Plan.} 	& 		12	& \textbf{12} \\
				
\midrule
% === OTHERS ==========================
\textbf{345} 	&& {\bf As a student I need to attend the customer meetings.} 	& 		6	& \textbf{6} \\

\textbf{344} 	&& {\bf As a student I need to attend the team building.} 	& 		7	& \textbf{9} \\
		
\textbf{327} 	&& {\bf As a student I need to attend the supervisor meeting. } 	& 		16	& \textbf{16} \\

\textbf{321} 	&& {\bf As a student I need to participate to lectures about team dynamics. } 	& 		32	& \textbf{25} \\
				&& Course of group dynamics Thu.	&  &  \\
				&& Summary of course and exchange learned.	&  &  \\
				

				
\hline
				&& \textbf{SUM:}		&		164	& \textbf{?}
 \\																			
\bottomrule[1mm]
\end{longtable}
