%actions.tex
\nextItem (1.2) Merge sprint chapters into Implementation chapter. & &
\nextItem (1.2) Attachments and references are supposed to be in appendix. & &
\nextItem (1.4) Include customer in the text, describe purpose and write why is it needed and what is the point of having such a product. & & 
\nextItem (1.5) Say what is the scope of terminology, add Digital Lighter there, and move it to the end & &
\nextItem (1.6) Do not use \emph{objectives} words for goal. & &
\nextItem (1.6.1) Be more specific, specific dates, requirements (instead of guidelines), customer satisfaction should be mention & &
\nextItem (14) Write reflection about personal goals & &
\nextItem (1.7.1) Write more information about Peder and move the section \emph{Customer} more up (part of general information) & &
\nextItem (1.7.2) Delete the part about intention for 5-7 students & &
\nextItem (1.3) Rewrite the title. & &
\nextItem (1.7.5) Surround table by text. & &
\nextItem (2.2) One can choose - We were choosing -- be more specific & &
\nextItem (2.2) Do not refer to methodology as a technique & &
\nextItem (3.1) Explain items of WBS and move the figure in the text & &
\nextItem (all) Table and Figures are with capital & &
\nextItem (3.3) An explanation for proactive and reactive measure is needed & &
\nextItem (3.3.1) Remove title, merge it to Risk management & &
\nextItem (3.4.3) Add supervisor collaboration & &
\nextItem (Table 3.4) Fill the spent time & &
\nextItem (3.5) Create a table summarizing what we use from Scrum. & &
\nextItem (3.7.2) Explain the length of sprints. & &
\nextItem (4.1) and (4.3) Add a reference & &
\nextItem (4.2) Remove title & &
\nextItem (4.3.2) Specific values for non-functional, remove N5, N6 & &
\nextItem (all) Use page when referencing. & &
\nextItem (sprints retrospective) Follow question (what went wrong, what went well, what should we start doing). & &
\nextItem (sprints) Better feedback from customer. & &
\nextItem (sprint stories) Explain hours in tables. & &
\nextItem (7.3) Rename to preliminary studies. & &
\nextItem (7.6) 
\nextItem (Figure 7.8) Reference the statistics. & &
\nextItem (7.6) Link risks. & &
\nextItem (7.7.2) Write better reflection. & &
