\newcommand{\meetingNumber}{6}
\newcommand{\meetingPlace} {Gloshaugen, Room}
\newcommand{\meetingDate}  {2013}
\newcommand{\meetingTime}  {18:00}
\newcommand{\membersPresent} {  Peder Kongelf,
                                Tomas Dohnalek,
                                Jan Bednarik,
                                Milos Jovac}
\newcommand{\membersMissing} {Agnethe Soraa}
\newcommand{\summary} {We started the meeting with the demonstration of our last Prototype 2 using the YouTube video. Then we proceeded to discussion about the UML diagrams used in the requirements section. The customer suggested us to not violate the UML standard and advised us to use the flow chart instead of the sequence diagram. The customer also gave us the advise about the use case diagram, we should simplify it by merging specific use cases. We do not need to do the time estimation unless the adviser strictly requires that. Customer strongly requires us not to implement the core image processing part ourselves but we should ask our supervisor who to talk about it with. Then we presented our Sprint 3 plan and the customer added a few stories regarding image processing for us to work on. Our server should process both real world and mock data. We also have to make make the prototype that would be able to recognize a few devices from light, map them in the grid and tell which color is placed in which field (2 x 2). We should design the application in a way that it could be scaled up so that one device screen could play more colors at once.
}
\newcommand{\nextMeeting} {3 October}
\newcommand{\meetingEnd} {19:15}
